A Toolbox for Manipulating and Assessing Color Palettes for Statistical Graphics

### 2019-06-25 pkg/colorspace/paper/Toolbox/slides.Rnw
add info about grDevices::hcl.colors
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@495 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

@@

\begin{itemize}
  \item Do not overestimate the effectiveness of color.
  \item Choose type of palette based on the data to be visualized.
  \item For areas use light colors (higher luminance, lower chroma).
  \item For points/lines darker colors are needed (lower luminance, higher chroma).
  \item For palettes with more colors stronger luminance contrasts are needed.
  \item Triangular chroma trajectories useful for distinguishing central colors.
\end{itemize}

>>>>

\subsection{Base R}

\begin{frame}
\frametitle{Base R}

\textbf{In 3.6.0:} All prespecified palettes also via \code{grDevices::hcl.colors()}.

\vspace*{-1.8cm}

\setkeys{Gin}{width=\textwidth}
<<hcl-colors, fig = TRUE, width = 11, height = 8>>=
hcl.swatch <- function(palette = hcl.pals(), n = 5, nrow = 11,
  border = if (n < 15) "black" else NA)
{
    cols <- sapply(palette, hcl.colors, n = n)
    ncol <- ncol(cols)
    nswatch <- min(ncol, nrow)

    par(mar = rep(0.1, 4),
        mfrow = c(1, min(10, ncol %/% nrow + 1)),
        pin = c(1, 0.5 * nswatch),
        cex = 0.7)

    while (length(palette)) {
        subset <- 1:min(nrow, ncol(cols))
        plot.new()
        plot.window(c(0, n), c(0, nrow + 1))
        text(0, rev(subset) + 0.1, palette[subset], adj = c(0, 0))
        y <- rep(subset, each = n)
        rect(rep(0:(n-1), n), rev(y), rep(1:n, n), rev(y) - 0.5,
             col = cols[, subset], border = border)
        palette <- palette[-subset]
        cols <- cols[, -subset]
    }

    par(mfrow = c(1, 1), mar = c(5.1, 4.1, 4.1, 2.1), cex = 1)
}
hcl.swatch()
@

@@

\textbf{Colors and palettes:}
\begin{itemize}
  \item Do not overestimate the effectiveness of color.
  \item Choose type of palette based on the data to be visualized.
  \item For areas use light colors (higher luminance, lower chroma).
  \item For points/lines darker colors are needed (lower luminance, higher chroma).
  \item For palettes with more colors stronger luminance contrasts are needed.
  \item Triangular chroma trajectories useful for distinguishing central colors.
\end{itemize}

\textbf{R packages:}
\begin{itemize}
  \item \pkg{colorspace} facilitates exploration, manipulation, and assessment.
  \item HCL approximations of palettes from \pkg{RColorBrewer}, \pkg{rcartocolor}, \pkg{scico}, \dots
  \item Prespecified palettes are also easily available in base R.
\end{itemize}
